\documentclass{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

\begin{document}

\part{Blaž Šnuderl}

\section{Work experience}

\begin{eventlist}

\item{March 2015 -- Current}
     {AppMonsta, San Francisco}
     {Data Engineer}

I am in charge of a data analytics pipeline and its API backend. We are collecting data from user phones and doing analytics on it. Our code analytics code is written in Spark/python and handles processing of about 200.000 unique daily devices. Backend is written in Django, with postgres and elasticsearch as databases.

\newline

\item{June 2014 -- August 2014}
     {Tridens, Maribor}
     {RoR development and CI}

My work consisted of two parts. First month I was assigned to set up continuous integration for a large Java Enterprise project, that previously had no automated tests. I refactored the project to use Maven for the whole process from compiling to deployment. Previously the project could only be run and deployed using Eclipse. I also set up a private Jenkins instance where project was being continuously tested. 
\newline
On my second month I joined a team developing a Ruby on Rails portal for a telecommunications company. My work consisted mostly of back end work. Some of the other stuff I ended working on was search with Solr and using Redis as a background job queue.

\item{July 2013 -- September 2013}
     {Frembassy, Ljubljana}
     {Web developer}
     
I was part of a small team working on a single page web application for a large automotive company. Client side code was written using the AngularJS framework. For back end we used Python running on Google App Engine. My work was evenly split between both front and back end work. I did everything from large code refactoring on the client side to creating new database models and constructing indexes on Google's Datastore.

\end{eventlist}


\section{Projects}

\begin{yearlist}

\item{2013}
     {Trainer Jim - Imagine Cup competition}
     {Gym application written in Ruby on Rails and Knockout. Made it to the finals in Slovenian Imagine cup competition.}

\end{yearlist}




\personal
    {Kuraltova, 14\newline 2000 -- Maribor}
    {+386 41 899 369}
    {snuderl@gmail.com}
    


\section{Education}

\begin{yearlist}

\item[Masters degree]{2012 -- 201?}
     {Computer science}
     {FERI, Maribor}

\item{2008 -- 2012}
     {Informatics}
     {FERI, Maribor}
     
\item{Summer 2012}
    {Summer school on Machine Learning}
    {FRI, Ljubljana}
     
\item[Coursera, edX]
    {Lifelong}
    {Online coursers (MOOC's)}
    {Finished multiple online coursers (MOOC's) on topics such as Machine Learning, Functional programming, Low level programming, probability.}

\end{yearlist} 


\section{Technology skills}

\begin{factlist}

\item{Proficient}
     {Python, Apache Spark, Django}

\item{Intermidiate:}
     {Functional Programming (Scala, Haskell, Lisp), Java, Relational databases (postgres), AWS, Web dev}
     
\item{Familiar:}
     {Machine Learning, Elasticsearch, Redis, Hadoop, Android}

\item{Buzzwords:}
     {Git, Unit testing, Continuous integration, Linux}

\end{factlist}

\section{Communication skills}

\begin{factlist}
\item{Slovenian}{Native speaker}
\item{English}{Fluent}
\item{German}{Basic}
\end{factlist}

\section{Links} 
Github: \href{https://github.com/snuderl}{\textbf{snuderl}} \newline
LinkedIn:  \href{https://www.linkedin.com/pub/bla\%C5\%BE-\%C5\%A1nuderl/25/679/b84}{\textbf{Blaž Šnuderl}} \newline
Stack Owerflow: \href{http://stackoverflow.com/users/928489/bla\%C5\%BE-\%C5\%A1nuderl}{\textbf{Blaž Šnuderl}}


\end{document}
